CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-09-17 codecheck-paper.tex
okay, no more citation hunting tonight...

  \begin{tabular}{lllp{9cm}} \toprule Certificate & Ref & Research
    area & Description \\ \midrule 2020-001 & \cite{cert-2020-001} &
    Machine learning & CODECHECK undertaken post acceptance of
    manuscript and before its publication in \textit{Gigascience}
    \cite{Piccolo2020-lo}.
    \\
    2020-002 & \cite{cert-2020-002} & neuroscience & Paper from 1997
                                                     showing
                                                     unsupervised
                                                     learning from
                                                     natural images
                                                     \cite{Hancock1992-mp}.
    \\
    2020-003 & \cite{cert-2020-003} & neuroscience &
                                                     Classic paper
                                                     from 1982 on
                                                     models of
                                                     associative
                                                     memory
                                                     \cite{Hopfield1982-mz}.
    (Simulation code was written specifically for this project.)\\
    2020-004 & \cite{cert-2020-004} & area & Barto \\
    2020-005 & \cite{cert-2020-005} & area & Larisch \\
    2020-006 & \cite{cert-2020-006} & area & Detorakis \\
    2020-007 & \cite{cert-2020-007} & area & in progress \\
    2020-008 & \cite{cert-2020-008} & Covid & Modelling of
    interventions on Covid  cases in the UK; checked as preprint (NOW REMOVED XXX)
    and now published \cite{Davies2020-vj} \\
    2020-009 & \cite{cert-2020-009} & Covid &  tracing \\
    2020-010 & \cite{cert-2020-010} & Covid &  report 9 \\
    2020-011 & \cite{cert-2020-011} & Covid & Modelling of Covid
    spread across Europe;  paper was checked when in press (now  published) \cite{Flaxman2020-yb}. \\
    2020-012 & \cite{cert-2020-012} & Covid &   Modelling of Covid spread across the USA; preprint currently review \cite{Unwin2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates.  An interactive version
  of this is available at \url{http://codecheck.org.uk/register}.  SJE
to complete...}
  \label{tab:register}
\end{table}

>>>>

  \begin{tabular}{llp{11cm}}
    \toprule
    Certificate & Research area & Description \\ \midrule
    2020-001 \cite{cert-2020-001} &
    Machine learning & CODECHECK undertaken post acceptance of
    manuscript and before its publication in \textit{Gigascience}
    \cite{Piccolo2020-lo}.
    \\
    2020-002  \cite{cert-2020-002} & neuroscience & Paper from 1997
 showing unsupervised learning from natural images \cite{Hancock1992-mp}.
 Code written for this project.
    \\
    2020-003  \cite{cert-2020-003} & neuroscience &
                                                     Classic paper
                                                     from 1982 on
                                                     models of
                                                     associative
                                                     memory
                                                     \cite{Hopfield1982-mz}.
    (Simulation code was written specifically for this project.)\\
    2020-004  \cite{cert-2020-004} & area & Cart-pole balancing problem solved using reinforcement learning \cite{Barto1983-rg}.  Code written for this reimplementation.\\
    2020-005  \cite{cert-2020-005} & area & Larisch \\
    2020-006  \cite{cert-2020-006} & area & Detorakis \\
    2020-007  \cite{cert-2020-007} & area & in progress \\
    2020-008  \cite{cert-2020-008} & Covid & Modelling of
    interventions on Covid  cases in the UK; checked as preprint (NOW REMOVED XXX)
    and now published \cite{Davies2020-vj} \\
    2020-009  \cite{cert-2020-009} & Covid &  tracing \\
    2020-010  \cite{cert-2020-010} & Covid &  report 9 \\
    2020-011  \cite{cert-2020-011} & Covid & Modelling of Covid
    spread across Europe;  paper was checked when in press (now  published) \cite{Flaxman2020-yb}. \\
    2020-012  \cite{cert-2020-012} & Covid &   Modelling of Covid spread across the USA; preprint currently review \cite{Unwin2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates.  An interactive version
  of this is available at \url{http://codecheck.org.uk/register}.  SJE
to complete...}
  \label{tab:register}
\end{table}
